---
title: "How to use Stcr"
author: "Eunmin Lee, "
date: "`r BiocStyle::doc_date()`"
package: "Stcr" 

abstract: |
  Description of your vignette
vignette: |
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document
---
```{r, echo=FALSE, results="hide", warning=FALSE, message=FALSE}
suppressPackageStartupMessages({
  library(Stcr)
})
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```
# Introduction

# Quick start
contig data preperation

```{r}
data("BC9_s1_contig")
data("BC9_s2_contig")
rownames(BC9_s1_contig)  = BC9_s1_contig$contig_id
rownames(BC9_s2_contig)  = BC9_s2_contig$contig_id
# 
BC9_s1_contig = subset(BC9_s1_contig, productive == "True")
BC9_s2_contig = subset(BC9_s2_contig, productive == "True")
sset_BC9_s1 <- new( 'StcrSet',
             contig = BC9_s1_contig,
             cellName = vector(),
             reductions = list(),
             ident = factor(),
             vdjMat = list(),
             meta.data = data.frame())
sset_BC9_s2 <- new( 'StcrSet',
                    contig = BC9_s2_contig,
                    cellName = vector(),
                    reductions = list(),
                    ident = factor(),
                    vdjMat = list(),
                    meta.data = data.frame())
```

or you could load your contig file using Load10xVDJ function

If you have more than one sample, you can attach their sampleID to the barcodes of the contig using SetSample function. Then these are merged to one StcrSet.
```{r}
sset_BC9_s1 = SetSample(sset_BC9_s1,sampleID = "s1")
sset_BC9_s2 = SetSample(sset_BC9_s2,sampleID = "s2")

sset_BC9 = MergeSamples(sset_BC9_s1, sset_BC9_s2)
```

We implemented to use a seurat object for any dimensional coordiate information of the cells and their meta.data.
```{r}
data("seurat_BC9")

seurat_BC9 = Seurat::RenameCells(object = seurat_BC9, new.names = gsub("^s(.)_([ ACGT]*)-1","s\\1-\\2", colnames(seurat_BC9)))

sset_BC9 = ImportSeurat(sset_BC9,seurat_BC9, version = "v3")
```
## PlotTCR
```{r}
sset_BC9@meta.data$target = rownames(sset_BC9@meta.data) %in% 
  sset_BC9@contig$cellName[sset_BC9@contig$v_gene == "TRAV41"]
PlotTCR(sset_BC9, group_by = "target", reduction = "tsne")
```
# SetVDJcountMat
```{r}
mat_AV = SetVDJcountMat(sset_BC9, chain= "TRA", v_gene = "AV")
mat_BV = SetVDJcountMat(sset_BC9, chain= "TRB", v_gene = "BV")
```

## PlotPairUsageHeatmap
```{r}
PlotPairUsageHeatmap(mat_AV, mat_BV, cell_ind = names(sset_BC9@ident)[sset_BC9@ident == 0])
```
# SetCDR3Mat
```{r}
cdr3_list = SetCDR3Mat(sset_BC9, chain1 = c("TRA"), chain2 = c("TRB"))
```

## PlotFancyChainUsage
```{r}
PlotFancyChainUsage(cdr3_list, cellLimit = 20)
```
# SetCDR3PairMat
```{r}
cdr3pair_list = SetCDR3PairMat(sset_BC9, cdr3_list)
```


## PlotFrequency
```{r}
PlotFrequency(cdr3pair_list, ident = sset_BC9@ident,
              chain1_v_gene = "(TRAV20|TRAV26|TRAV12)",
              chain2_v_gene = "(TRBV9|TRBV20)")
```
## PlotPorportionsByGene
```{r}
PlotProportionsByGene(cdr3pair_list, ident = sset_BC9@ident,
                            chain1_v_gene = "(TRAV20|TRAV26|TRAV12)",
                            chain2_v_gene = "(TRBV9|TRBV20)")
```
## PlotClonotypes
```{r}
PlotClonotypes(cdr3pair_list, ident = sset_BC9@ident, cellLimit = 10)
```
## PlotDiversity
```{r}
PlotDiversity(cdr3pair_list, ident = sset_BC9@ident )
```
## PlotOverlapHeatmap
```{r}
PlotOverlapHeatmap(cdr3pair_list, ident = sset_BC9@ident, compute = "geomean")
```

# Session info

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

# References